### 2016-03-14 paper/introduction.tex

Parallel computation offers tremendous potential for Computer Vision. As
image sensing technologies have gone through revolutions, we are in
ever growing demands in solving very large problems. One may need to
apply image denoising to 50 Megapixel images from latest digital
SLRs (e.g., Canon EOS 5DS), stitch thousands of images to generate gigapixel
panoramas~\cite{kopf2007capturing}, or solve volumetric reconstruction and
segmentation problems over a billion ($=1024^3$)
voxels~\cite{hane2013joint}.
%
%% However, state-of-the-art algorithms are still inherently
%% sequential in many Computer Vision problems. Take a Fusion Move
%% method
%% (FM)~\cite{fusion_flow,fusion_moves_for_markov_random_field_optimization,second_order_stereo}
%% for example, which has been one of the most effective techniques
%% for Markov Ran- dom Field (MRF) inference, including the above
%% problems like image denoising, image stitching, or volumetric
%% reconstruction. It sequentially improves solution by fusing the
%% current solution with a solution proposal. Its successful applica-
%% tions go beyond and also cover optical flow, stereo, image
%% inpainting, or image segmentation
%% problems~\cite{fusion_moves_for_markov_random_field_optimization} .
%
The MAP framework, which can be formulated as a Markov Random Field
(MRF) in many low-level Computer Vision problems, provides a universal
and powerful way to solve these problems. However, state-of-the-art
algorithms for MRF inference are still inherently sequential. Take a
Fusion Move method
(FM)~\cite{fusion_flow,fusion_moves_for_markov_random_field_optimization,second_order_stereo}
for example, which has been one of the most effective techniques for
MRF inference, it sequentially improves solution by fusing the current solution with
a solution proposal. Its successful applications cover not only above
problems, but also popular problmes like optical flow, stereo, image
inpainting, or image segmentation
problems~\cite{fusion_moves_for_markov_random_field_optimization}.

@@

We have evaluated the effectiveness of our approach over three problems
in Computer Vision, stereo, optical flow, and layered
depthmap estimation.
%
%Our approach outperforms all the other competing methods, especially for
%challenging problems with a large label space.
%
%Our idea is very simple. We believe that the method is easily
%reproducible with minimal coding
%
We believe that the method can be intergrated into existing algorithms
with minimal coding, and would have immediate impact on numerous
Computer Vision researchers or engineers.

>>>>

Parallel computation offers tremendous potential for Computer Vision. As
image sensing technologies have gone through revolutions, we are in
ever growing demands in solving very large problems. One may need to
apply image denoising to 50 Megapixel images from latest digital
SLRs (e.g., Canon EOS 5DS), stitch thousands of images to generate gigapixel
panoramas~\cite{kopf2007capturing}, or solve volumetric reconstruction and
segmentation problems over a billion ($=1024^3$)
voxels~\cite{hane2013joint}.
%
%% However, state-of-the-art algorithms are still inherently
%% sequential in many Computer Vision problems. Take a Fusion Move
%% method
%% (FM)~\cite{fusion_flow,fusion_moves_for_markov_random_field_optimization,second_order_stereo}
%% for example, which has been one of the most effective techniques
%% for Markov Ran- dom Field (MRF) inference, including the above
%% problems like image denoising, image stitching, or volumetric
%% reconstruction. It sequentially improves solution by fusing the
%% current solution with a solution proposal. Its successful applica-
%% tions go beyond and also cover optical flow, stereo, image
%% inpainting, or image segmentation
%% problems~\cite{fusion_moves_for_markov_random_field_optimization} .
%
The MAP framework, which can be formulated as a Markov Random Field
(MRF) in many low-level Computer Vision problems, provides a universal
and powerful way to solve these problems. However, state-of-the-art
algorithms for MRF inference are still inherently sequential. Take a
Fusion Move method
(FM)~\cite{fusion_flow,fusion_moves_for_markov_random_field_optimization,second_order_stereo}
for example, which has been one of the most effective techniques for
MRF inference, it sequentially improves solution by fusing the current solution with
a solution proposal. Its successful applications cover not only above
problems, but also popular problems like optical flow, stereo, image
inpainting, or image segmentation
problems~\cite{fusion_moves_for_markov_random_field_optimization}.

@@

We have evaluated the effectiveness of our approach over three problems
in Computer Vision, stereo, optical flow, and layered
depthmap estimation.
%
%Our approach outperforms all the other competing methods, especially for
%challenging problems with a large label space.
%
%Our idea is very simple. We believe that the method is easily
%reproducible with minimal coding
%
We believe that the method can be integrated into existing algorithms
with minimal coding, and would have immediate impact on numerous
Computer Vision researchers or engineers.
